### 2023-08-15 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
edited up to section 2

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/SM}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }
%
\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\
%
 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Y.-N. Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
% %Author names go here instead of "Full name", etc.
%
\includegraphics{head_foot/dates} & \noindent\normalsize{We numerically
  study the hydrodynamics of multicomponent vesicles in two strongly
  confining geometries. This serves as a simplified model for red blood
  cells passing through extreme constrictions. We propose a new bending
  modulus parameterization so that it remains positive for all values of
  the lipid phase parameter. For a multicomponent vesicle passing
  through a stenosis, we correlate the lipid phase coarsening, the
  lubrication layer properties (size and flow profile), the excess
  pressure, and the tank-treading velocity of the membrane. For a
  multicomponent vesicle passing through a contracting channel, we find
  that the lipid always phase separates so that the vesicle is stiffer
  in the front as it passes through the constriction. For both cases of
  confinement we find that the lipid coarsening is arrested under strong
  confinement, and proceeds with high rate upon relief from extreme
  confinement. The results may be useful for efficient sorting lipid
  domains using microfluidic flows by controlled release of vesicles
  passing through strong confinement. } \\
  %The abstrast goes here instead of the text "The abstract should
  %be..."
%
\end{tabular}
%
 \end{@twocolumnfalse} \vspace{0.6cm}
]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

@@

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, as the basic structural units for
compartmentalizing biological systems, have been observed to contain a
vast array of proteins and different lipid species, that phase-separate
and form domains or rafts, resulting in spatial variations in material
properties such as bending stiffness. Synthetic multicomponent vesicles,
self-enclosed lipid bilayer membranes composed of different lipid
species, have been used to study the rich patterns and accompanying
morphologies that emerge from elastic heterogeneity in the membrane. In
a quiescent environment, such elastic heterogeneity gives rise to
wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci}, adhesion
and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely related to
cellular budding and fission processes~\cite{Rauch2000_BiophysJ} as well
as in cellular adhesion and fusion~\cite{Takeda2003_PNAS}.

The hydrodynamics of a single-component vesicle is characterized by
parameters such as the capillary number, reduced volume, and confinement
ratio \cite{Abreu2014_ACI}. Such characterization is often useful for
inferring fluid and material properties.
%Understanding these dynamics is critical to understanding the biophysics of red blood cells (RBCs) in blood flow. 
For example, a vesicle's reduced volume and viscosity contrast determine
if it undergoes tank-treading, swinging, or tumbling in a shear
flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
these shapes include axisymmetric bullets or parachutes, and asymmetric
parachutes. Recently, characterization of vesicles suspended in a
channel or pipe flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020,
qua-gan-you2021, abb-far-nai-ezz-ben-mis2022,
wan-ii-sug-nod-jin-liu-che-gon2023} showed more exotic vesicle
hydrodynamics such as snaking and swirling behaviors in croissant and
slipper shapes.

Under a linear shear flow, a multicomponent vesicle exhibits more exotic
dynamics in both shape and membrane
composition~\cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,
Cox2015_Nonlinearity, liu-mar-li-vee-low2017, Tusch2018_PRF,
Gera2018_SoftMatter, ger-sal-spa2022} than a single-component vesicle.
For example, multicomponent vesicles under a background flow often
exhibit highly complex morphologies, leading to vesicle budding. The
hydrodynamics of these multicomponent vesicles include phase treading,
tumbling with no viscosity contrast, swinging, budding, and
fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
ger-sal-spa2022, lip1992, urs-klu-phi2009}. Through numerical
investigations,~\citet{liu-mar-li-vee-low2017} identified several key
dimensionless numbers, including the reduced area, capillary number, and
the floppy-to-stiff ratio to characterize various dynamics of a
multicomponent vesicle in an unbounded linear shear flow. In addition to
the aforementioned numerical studies, these dynamics have been observed
in experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
dre-jah-bob-spa-gop2021}.

%
%Sohn et al. (2010) studied two-dimensional multicomponent vesicles in a background shear flow, along with the evolution of distinct surface phases, finding highly complex morphologies and dynamics for highly deformed vesicles. Smith & Uspal (2007) showed using dissipative particle dynamics simulations that a shear flow can be used to separate buds from a multicomponent vesicle. The influence of both bending rigidity and spontaneous curvature variation on the equilibrium shape of a vesicle has also been investigated (Cox & Lowengrub 2015). Subsequent boundary integral simulations by Liu et al. (2017) showed a transition from tumbling to tank-treading to ‘phase-treading’ of the constituents along the surface upon increasing the shear rate. Analytic results have also shown that a variation of bending rigidity along a surface can induce migration in tank-treading vesicles (Olla 2011). Synthetic systems have also been fruitful for testing theoretical predictions. Experiments using a two-phase lipid vesicle in such a flow as a simplified model of red blood cell dynamics showed similarly complex features (Tusch et al. 2018). Gera & Salac (2018b) then used simulations to probe a wide array of morphological changes due to spatially varying bending stiffness and line tension between two lipid phases. The phase separation process itself is naturally of great interest, and experiments have been used to study spinodal decomposition and viscous fingering along membrane surfaces (Veatch & Keller 2003; Lowengrub, Rätz & Voigt 2009; Marenduzzo & Orlandini 2013; Stanich et al. 2013).
%
%
%Groups have also studied the behaviors of a vesicle that is composed of
%different types of lipids and proteins. The presence of different lipid
%species has been used to model different processes including the bending
%stiffness, spontaneous curvature, and adhesion
%potential~\cite{zha-das-du2010, tan-yan-ima2011}. The dynamics of these
%multicomponent vesicles include phase treading, tumbling with no
%viscosity contrast, swinging, budding, and
%fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
%ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
%aforementioned numerical studies, these dynamics have been observed in
%experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
%dre-jah-bob-spa-gop2021}.
%

Hydrodynamics of vesicles in extreme confinement has been studied as a
model system for red blood cells (RBCs) squeezing through small
capillaries (of sub-micron size in diameter) under a pressure difference
\cite{Freund2013_PoF, LuPeng2019_PoF, che-lyu-jae-leo2020,
gur-pak-tay-siv-sac2023}. Membrane permeability has been incorporated to
examine the single-component vesicle hydrodynamics. In the absence of an
osmotic gradient, the semipermeable vesicle is affected by water
influx/efflux over a sufficiently long time or under a strong
confinement \cite{qua-gan-you2021}. Numerical simulations illustrate
that a vesicle with moderate membrane permeability can go through a
strong confinement much more easily, and can restore its water content
within a very short time after its passage through the strong
confinement. These results imply that the membrane permeability may be
inferred from vesicle hydrodynamics under a strong confinement.
Motivated by these results, in this work we seek to investigate how
strong confinement may affect the hydrodynamics of a multicomponent
vesicle? This question is highly relevant to hydrodynamics of cells in a
confinement, and to our knowledge has not been well studied.
\citet{ram-kom-sek-ima2010} reported that confinement reduces the
effective diffusion coefficient of the concentration fluctuation in
multicomponent membranes. How is such reduced concentration diffusion
coefficient reflected in the hydrodynamics of multicomponent vesicles
under strong confinement?

In this paper, we use numerical simulations and lubrication analysis
\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} to
investigate the effect of strong confinement on a two-dimensional
multicomponent vesicle.  In particular we show how the vesicle's reduced
area and its lipid composition affect the dynamics in two strongly
confined geometries.
%
The remainder of the paper is organized as follows.
Section~\ref{sec:Formulation} describes the model for the
two-dimensional multicomponent vesicle. We introduce a new
parameterization of the bending modulus that is necessary to avoid
unphysical negative bending stiffness.
Section~\ref{sec:NumericalMethods} describes numerical methods and also
defines the techniques we use to define the excess pressure, lubrication
layer width, and tank-treading velocity. Section~\ref{sec:results}
demonstrates the effects of strong confinement on multicomponent
vesicles. Finally, concluding remarks are made in
Section~\ref{sec:conclusion}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Formulation}Formulation}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematic}\small A multicomponent vesicle
  suspended in a strongly-confined stenosis. The color is the
  dimensionless stiffness which varies from $b_{\min} = 0.1$ to
  $b_{\max} = 1$. The vesicle dynamics are determined by a combination
  of phase, bending, and tension energies, and an imposed flow (blue
  arrows). The lubrication layer (gray region), defined in
  Section~\ref{sec:LL} plays a key role in the vesicle dynamics.}
%  \caption{\label{fig:schematic}\small A single multicomponent vesicle
%  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
%  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
%  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
%  are the ``floppy'' regions corresponding to the minimum bending
%  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
%  combination of phase, bending, and tension energies, and an imposed
%  flow on $\Gamma$. }
\end{figure}
We consider a single multicomponent vesicle $\omega$ with boundary
$\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with
boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid is assumed to
have zero Reynolds number and is therefore governed by the
incompressible Stokes equations
\begin{align}
  \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
    \quad \xx \in \Omega \backslash \gamma,
\end{align}
where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
we require that the velocity is continuous and locally inextensible, and
the membrane and hydrodynamic forces balance
\begin{align}
  \llbracket \uu \rrbracket = 0, \quad 
  \nabla_{\gamma} \cdot \uu = 0, \quad
  \llbracket \TT\nn \rrbracket = \ff, \quad \xx \in \gamma,
\end{align}
where $\ff$ is the total membrane force and $\nn$ is the outward unit
normal of $\gamma$. Parameterizing $\gamma$ as $\xx(s,t)$, where $s$ is
arclength and $t$ is time, the no-slip boundary condition is
$\frac{d\xx}{dt} = \uu(\xx)$. Along the solid wall $\Gamma$, we impose a
Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
\begin{align}
  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel.

We nondimensionalize the governing equations with a characteristic
length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} =
10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
resulting bending relaxation time scale is $\mu R_0^3/b_{\max} = 0.5$~s,
the velocity scale is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure
scale is $b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is
$b_{\max}/R_0^2 = 10^{-7}$~N/m. The dimensionless parameters regarding
the vesicle properties are the reduced area $\alpha = 4\pi A/L^2$, where
$A$ and $L$ are the vesicle's area and length, respectively, and the
floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
flows in channels, we also define a maximum imposed velocity, $U$, which
sets the capillary number $Ca = U R_{0}^{2} \mu/b_{\max}$, and $W/R_0$
is the dimensionless width of the channel at the inlet and outlet.
Finally, the Peclet number of the lipid dynamics is taken to be $Pe = 1$
which results in a diffusion time scale of $2 \times 10^{-4}$~s.
Therefore, phase separation occurs at a rate three orders of magnitude
faster than vesicle relaxation. The effect of the Peclet number has been
examined~\cite{liu-mar-li-vee-low2017, soh-tse-li-voi-low2010}, and it
has no qualitative effect on the vesicle dynamics. From this point
onwards, all equations are dimensionless.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constitutive equations\label{subsec:const_eq}}
Using the model first introduced by~\citet{liu-mar-li-vee-low2017}, the
membrane forces depend on the Helfrich energy, line tension, and phase
energy. The phase and bending energies are coupled through the bending
modulus. In particular, the individual energies are
\begin{align}
  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \quad
  E_t = \int_{\gamma} \sigma \, ds, \\
  E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
  f(u) +\frac{\epsilon^2}{2}|\nabla_\gamma u|^2\right) \, ds,
  \label{eqn:PhaseEnergy}
\end{align}
where $u$ is the dimensionless lipid concentration, $b(u)$ is the
lipid-dependent bending modulus, $\sigma$ is the vesicle's tension,
$\kappa$ is the membrane curvature, and $f(u) = \frac{1}{4}u^2(1-u)^2$
is a double-well potential with local minimums at $u=0$ and $u=1$. The
parameter $\epsilon \ll 1$ sets the size of the transition region of
$u$, and the parameter $a$ is line tension scaled by the characteristic
bending stiffness. All simulations use the parameter values
$\epsilon=100$ and $a=0.04$. The resulting membrane forces are
\begin{align}
  \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
    \left(b(u) \kappa^2 \ss\right)_s, \\
  \ff_t &= (\sigma \ss)_s, \\
  \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s,
\end{align}
where $\ss$ is the unit tangent vector of $\gamma$.

>>>>

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/SM}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }
%
\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\
%
 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Y.-N. Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
% %Author names go here instead of "Full name", etc.
%
\includegraphics{head_foot/dates} & \noindent\normalsize{We numerically
  study the hydrodynamics of multicomponent vesicles in two strongly
  confining geometries. This serves as a simplified model for red blood
  cells undergoing large deformations when passing through extreme
  constrictions. We propose a new bending modulus parameterization that
  is positive for all values of the lipid phase parameter. For a
  multicomponent vesicle passing through a stenosis, we correlate the
  lipid phase coarsening, the lubrication layer properties (size and
  flow profile), the excess pressure, and the tank-treading velocity of
  the membrane. For a multicomponent vesicle passing through a
  contracting channel, we find that the lipid always phase separates so
  that the vesicle is stiffer in the front as it passes through the
  constriction. For both cases of confinement we find that the lipid
  coarsening is arrested under strong confinement, and proceeds with
  high rate upon relief from extreme confinement. The results may be
  useful for efficient sorting lipid domains using microfluidic flows by
  controlled release of vesicles passing through strong confinement.} \\
  %The abstrast goes here instead of the text "The abstract should
  %be..."
%
\end{tabular}
%
 \end{@twocolumnfalse} \vspace{0.6cm}
]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

@@

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, the basic structural units for compartmentalizing
biological systems, have been observed to contain a vast array of
proteins and different lipid species that phase-separate and form
domains or rafts, resulting in spatial variations in material properties
such as bending stiffness. Synthetic multicomponent vesicles,
self-enclosed lipid bilayer membranes composed of different lipid
species, have been used to study the rich patterns and accompanying
morphologies that emerge from elastic heterogeneity in the membrane. In
a quiescent environment, such elastic heterogeneity gives rise to
wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci}, adhesion
and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely related to
cellular budding and fission processes~\cite{Rauch2000_BiophysJ} as well
as in cellular adhesion and fusion~\cite{Takeda2003_PNAS}.

The hydrodynamics of a single-component vesicle is characterized by
parameters such as the capillary number, reduced volume, and confinement
ratio~\cite{Abreu2014_ACI}. Such characterization is often useful for
inferring fluid and material properties.
%Understanding these dynamics is critical to understanding the biophysics of red blood cells (RBCs) in blood flow. 
For example, a vesicle's reduced volume and viscosity contrast determine
if it undergoes tank-treading, swinging, or tumbling in a linear shear
flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
these shapes include axisymmetric bullets or parachutes, and asymmetric
parachutes. Recently, characterization of vesicles suspended in a
channel or pipe flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020,
qua-gan-you2021, abb-far-nai-ezz-ben-mis2022,
wan-ii-sug-nod-jin-liu-che-gon2023} showed more exotic vesicle
hydrodynamics such as snaking and swirling behaviors in croissant and
slipper shapes.

Under a linear shear flow, a multicomponent vesicle exhibits more exotic
dynamics in both shape and membrane composition than a single-component
vesicle~\cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,
Cox2015_Nonlinearity, liu-mar-li-vee-low2017, Tusch2018_PRF,
Gera2018_SoftMatter, ger-sal-spa2022}. For example, multicomponent
vesicles under a background flow often exhibit highly complex
morphologies, leading to vesicle budding. The hydrodynamics of these
multicomponent vesicles include phase treading, tumbling with no
viscosity contrast, swinging, budding, and
fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
ger-sal-spa2022, lip1992, urs-klu-phi2009}. Through numerical
investigations,~\citet{liu-mar-li-vee-low2017} identified several key
dimensionless numbers, including the reduced area, capillary number, and
the floppy-to-stiff ratio to characterize various dynamics of a
two-dimensional multicomponent vesicle in an unbounded linear shear
flow. In addition to the aforementioned numerical studies, these
dynamics have been observed in experiments~\cite{bag-sun2009,
yan-ima-tan2010, yan-ima-tan2008, dre-jah-bob-spa-gop2021}.

%
%Sohn et al. (2010) studied two-dimensional multicomponent vesicles in a
%background shear flow, along with the evolution of distinct surface
%phases, finding highly complex morphologies and dynamics for highly
%deformed vesicles. Smith & Uspal (2007) showed using dissipative
%particle dynamics simulations that a shear flow can be used to separate
%buds from a multicomponent vesicle. The influence of both bending
%rigidity and spontaneous curvature variation on the equilibrium shape
%of a vesicle has also been investigated (Cox & Lowengrub 2015).
%Subsequent boundary integral simulations by Liu et al. (2017) showed a
%transition from tumbling to tank-treading to ‘phase-treading’ of the
%constituents along the surface upon increasing the shear rate. Analytic
%results have also shown that a variation of bending rigidity along a
%surface can induce migration in tank-treading vesicles (Olla 2011).
%Synthetic systems have also been fruitful for testing theoretical
%predictions. Experiments using a two-phase lipid vesicle in such a flow
%as a simplified model of red blood cell dynamics showed similarly
%complex features (Tusch et al. 2018). Gera & Salac (2018b) then used
%simulations to probe a wide array of morphological changes due to
%spatially varying bending stiffness and line tension between two lipid
%phases. The phase separation process itself is naturally of great
%interest, and experiments have been used to study spinodal
%decomposition and viscous fingering along membrane surfaces (Veatch &
%Keller 2003; Lowengrub, Rätz & Voigt 2009; Marenduzzo & Orlandini 2013;
%Stanich et al. 2013).
%
%
%Groups have also studied the behaviors of a vesicle that is composed of
%different types of lipids and proteins. The presence of different lipid
%species has been used to model different processes including the
%bending stiffness, spontaneous curvature, and adhesion
%potential~\cite{zha-das-du2010, tan-yan-ima2011}. The dynamics of these
%multicomponent vesicles include phase treading, tumbling with no
%viscosity contrast, swinging, budding, and
%fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
%ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
%aforementioned numerical studies, these dynamics have been observed in
%experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
%dre-jah-bob-spa-gop2021}.
%

Hydrodynamics of vesicles in extreme confinement have been studied as a
model system for red blood cells (RBCs) squeezing through small
capillaries (of sub-micron size in diameter) under a pressure
difference~\cite{Freund2013_PoF, LuPeng2019_PoF, che-lyu-jae-leo2020,
gur-pak-tay-siv-sac2023}. Membrane permeability has been incorporated to
examine the single-component vesicle hydrodynamics. In the absence of an
osmotic gradient, the semipermeable vesicle is affected by water
influx/efflux over a sufficiently long time or under a strong
confinement~\cite{qua-gan-you2021}. Numerical simulations illustrate
that a vesicle with moderate membrane permeability can go through a
strong confinement much more easily, and can restore its water content
within a very short time after its passage through the strong
confinement. These results imply that the membrane permeability may be
inferred from vesicle hydrodynamics under a strong confinement.
Motivated by these results, in this work we seek to investigate how
strong confinement may affect the hydrodynamics of a multicomponent
vesicle. This question is highly relevant to hydrodynamics of cells in a
confinement, and to our knowledge has not been well studied.
\citet{ram-kom-sek-ima2010} reported that confinement reduces the
effective diffusion coefficient of the concentration fluctuation in
multicomponent membranes. How is such a reduced concentration diffusion
coefficient reflected in the hydrodynamics of multicomponent vesicles
under strong confinement?

In this paper, we use numerical simulations and lubrication
analysis~\cite{YoungStone2017_PRF,
mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} to
investigate the effect of strong confinement on a two-dimensional
multicomponent vesicle. In particular we show how the vesicle's reduced
area and its lipid composition affect the dynamics in two strongly
confined geometries.
%
The remainder of the paper is organized as follows.
Section~\ref{sec:Formulation} describes the model for the
two-dimensional multicomponent vesicle. We introduce a new
parameterization of the bending modulus that is necessary to avoid
unphysical negative bending stiffness.
Section~\ref{sec:NumericalMethods} describes numerical methods and also
defines the techniques we use to define the excess pressure, lubrication
layer width, and tank-treading velocity. Section~\ref{sec:results}
demonstrates the effects of strong confinement on multicomponent
vesicles. Finally, concluding remarks are made in
Section~\ref{sec:conclusion}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Formulation}Formulation}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematic}\small A multicomponent vesicle
  suspended in a strongly-confined stenosis. The color is the
  dimensionless stiffness which varies from $b_{\min} = 0.1$ to
  $b_{\max} = 1$. The vesicle dynamics are determined by a combination
  of phase, bending, and tension energies, and an imposed flow (blue
  arrows). The lubrication layer (gray region), defined in
  Section~\ref{sec:LL}, plays a key role in the vesicle dynamics.}
\end{figure}
We consider a single multicomponent vesicle $\omega$ with boundary
$\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with
boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid is assumed to
have zero Reynolds number and is therefore governed by the
incompressible Stokes equations
\begin{align}
  \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
    \quad \xx \in \Omega \backslash \gamma,
\end{align}
where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
we require that the velocity is continuous and locally inextensible, and
the membrane and hydrodynamic forces balance
\begin{align}
  \llbracket \uu \rrbracket = 0, \quad 
  \nabla_{\gamma} \cdot \uu = 0, \quad
  \llbracket \TT\nn \rrbracket = \ff, \quad \xx \in \gamma,
\end{align}
where $\ff$ is the total membrane force and $\nn$ is the outward unit
normal of $\gamma$. Parameterizing $\gamma$ as $\xx(s,t)$, where $s$ is
arclength and $t$ is time, the no-slip boundary condition is
$\frac{d\xx}{dt} = \uu(\xx)$. Along the solid wall $\Gamma$, we impose a
Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet
\begin{align}
  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $y \in [-W,W]$. $\UU$ is zero along the top and bottom of the
channel.

We nondimensionalize the governing equations with a characteristic
length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} =
10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
resulting bending relaxation time scale is $\mu R_0^3/b_{\max} = 0.5$~s,
the velocity scale is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure
scale is $b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is
$b_{\max}/R_0^2 = 10^{-7}$~N/m. The dimensionless parameters regarding
the vesicle properties are the reduced area $\alpha = 4\pi A/L^2$, where
$A$ and $L$ are the vesicle's area and length, respectively, and the
floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
flows in channels, we also define a maximum imposed velocity, $U$, which
sets the capillary number $Ca = U R_{0}^{2} \mu/b_{\max}$, and $W/R_0$
is the dimensionless width of the channel which varies in both examples
we consider. Finally, the Peclet number of the lipid dynamics is taken
to be $Pe = 1$ which results in a diffusion time scale of $2 \times
10^{-4}$~s. Therefore, phase separation occurs at a rate three orders of
magnitude faster than vesicle relaxation. The effect of the Peclet
number has been examined~\cite{liu-mar-li-vee-low2017,
soh-tse-li-voi-low2010}, and it has no qualitative effect on the vesicle
dynamics. From this point onwards, all equations are dimensionless.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constitutive equations\label{subsec:const_eq}}
Using the model first introduced by~\citet{liu-mar-li-vee-low2017}, the
membrane forces depend on the Helfrich energy, line tension, and phase
energy. The phase and bending energies are coupled through the bending
modulus. In particular, the individual energies are
\begin{align}
  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \quad
  E_t = \int_{\gamma} \sigma \, ds, \\
  E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
  f(u) +\frac{\epsilon^2}{2}|\nabla_\gamma u|^2\right) \, ds,
  \label{eqn:PhaseEnergy}
\end{align}
where $u$ is the dimensionless lipid concentration, $b(u)$ is the
lipid-dependent bending modulus, $\sigma$ is the membrane tension,
$\kappa$ is the membrane curvature, and $f(u) = \frac{1}{4}u^2(1-u)^2$
is a double-well potential with local minimums at $u=0$ and $u=1$. The
parameter $\epsilon \ll 1$ sets the size of the transition region of
$u$, and the parameter $a$ is line tension scaled by the characteristic
bending stiffness. All simulations use the parameter values
$\epsilon=100$ and $a=0.04$. The resulting membrane forces are
\begin{align}
  \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
    \left(b(u) \kappa^2 \ss\right)_s,  \quad
  \ff_t = (\sigma \ss)_s, \\
  \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s,
\end{align}
where $\ss$ is the unit tangent vector of $\gamma$.

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic since $b(u) < 0$ if $u > (1 - \beta)^{-1}$,
and such values of $u$ are possible when $\beta \ll 1$, $Ca \gg 1$, or
the vesicle is confined to a narrow region. This behavior is
demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
floppy-to-stiff ratio $\beta = 10^{-1}$. Using the linear bending model
in Equation~\eqref{eqn:linearBending}, the lipid concentration achieves
a maximum value of $u \approx 1.5$ which results in an instability that
is formed by the resulting unphysical negative bending stiffness. To
rectify this issue, we parameterize the bending modulus with the sigmoid
function
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, b(u) remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). This new bending model is validated in
Section~\ref{sec:validation}.
%To demonstrate the necessity of this new bending model, we consider a
%multicomponent vesicle in strong confinement with both bending
%models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
%stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
%model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
%maximum value of $u \approx 1.002$ which results in a minimum bending
%stiffness of $b(u) \approx \beta$. However, if we use the linear
%bending model~\eqref{eqn:linearBending}, the lipid concentration
%achieves a maximum value of $u \approx 1.52$ which results in an
%unphysical negative bending stiffness of $b(u) \approx -0.5$. The
%corresponding vesicle shape is in Figure~\ref{fig:concModels}(b), and
%the instability caused by the negative bending stiffness is near the
%region with negative curvature.
